Volatility Metric to Detect Anomalies in Source Code Repositories

### 2021-09-13 paper/article.tex
edited

\documentclass[anonymous,sigconf,10pt,nonacm=true]{acmart}
\title{Volatility Metric to Detect Anomalies in Source Code Repositories}
\author{Yegor Bugayenko}{}{}
\email{yegor.bugayenko@huawei.com}
\affiliation{%
  \institution{Huawei Technologies Co., Ltd.}
  \city{Moscow, Russia}
}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
% \setcopyright{acmcopyright}
% \copyrightyear{2020}
% \acmYear{2020}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
abandoned or even dead. It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
The metric may be used for earlier detection of code maintenance anomalies
and helping software developers make the decision of splitting the repository
into smaller ones in order to prevent maintainability issues.
\end{abstract}
\maketitle

@@

Most software development projects keep their source code in Git~\citep{loeliger2012},
which is the de-facto standard in the industry at the moment, or similar
version control systems. Every system, including open
source products like Git, Subversion, and Mercurial, and commerical tools
like Borland StarTeam\texttrademark{} or IBM ClearCase\texttrademark{}
have the same feature: keeping track of the changes
made to the source code files, also known as ``logs.''

@@

\begin{figure}[h]
  \input{files-64.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 64)}
  \label{fig:1}
\end{figure}

@@

\begin{figure}[h]
  \input{bytes-64.tex}
  \caption{The relationship between the size of the Git repository in bytes and its Volatility ($Z$ is set to 64)}
  \label{fig:2}
\end{figure}

@@

\begin{figure}[h]
  \input{files-32.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 32)}
  \label{fig:3}
\end{figure}

@@

\begin{figure}[h]
  \input{files-128.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 128)}
  \label{fig:4}
\end{figure}

>>>>

\documentclass[sigplan,10pt,nonacm=true]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}

\title{Volatility Metric to Detect Anomalies in Source Code Repositories}
\author{Yegor Bugayenko}{}{}
\email{yegor256@gmail.com}
\affiliation{\institution{}\city{Moscow}\country{Russia}}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
% \setcopyright{acmcopyright}
% \copyrightyear{2020}
% \acmYear{2020}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{tex/total}
\begin{document}
\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
abandoned or even dead. It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
The metric may be used for earlier detection of code maintenance anomalies
and helping software developers make the decision of splitting the repository
into smaller ones in order to prevent maintainability issues.
\end{abstract}
\maketitle

@@

Most software development projects keep their source code in Git~\citep{loeliger2012},
which is the de-facto standard in the industry at the moment, or similar
version control systems. Every system, including open
source products like Git, Subversion, and Mercurial, and commercical tools
like StarTeam\texttrademark{} or ClearCase\texttrademark{}
have the same feature: keeping track of the changes
made to the source code files, also known as ``logs.''

@@

\begin{figure}[h]
  \input{tex/files-64.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 64)}
  \label{fig:1}
\end{figure}

@@

\begin{figure}[h]
  \input{tex/bytes-64.tex}
  \caption{The relationship between the size of the Git repository in bytes and its Volatility ($Z$ is set to 64)}
  \label{fig:2}
\end{figure}

@@

\begin{figure}[h]
  \input{tex/files-32.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 32)}
  \label{fig:3}
\end{figure}

@@

\begin{figure}[h]
  \input{tex/files-128.tex}
  \caption{The relationship between the number of files in the repository and its Volatility ($Z$ is set to 128)}
  \label{fig:4}
\end{figure}
